---
title: "farsTrialPackage_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{farsTrialPackage_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Vignette: Exploring Traffic Accidents Data with fars R Package

## Introduction

The 'fars' package in R provides functions to explore and analyze data from the Fatality Analysis Reporting System (FARS), which contains data on fatal traffic accidents in the United States. This vignette will guide you through the usage of key functions in the 'fars' package.

## 1. Reading FARS Data

The `fars_read` function reads FARS data from a CSV file. It ensures the file exists and loads the data into a tibble, providing a streamlined interface for data access.

```{r}
#Load the library
library(farsTrialPackage)

# Example usage of fars_read function
data <- fars_read("accident_2013.csv")
```

## 2. Mapping Traffic Accidents by State and Year

The fars_map_state function visualizes traffic accidents on a map for a specific state and year. It plots accident locations on a map of the United States.

```{r}
# Example usage of fars_map_state function
fars_map_state(10, 2013)  # Plot accidents in state number 10 for year 2020

```
